%!TEX root = ../main.tex

\section*{Acknowledgments}

We are grateful to members of the Segrè lab for helpful discussions and for feedback on the manuscript. This work was partially funded by grants from the National Institutes of Health (National Institute of General Medical Sciences, award R01GM121950; National Institute of Dental and Craniofacial Research, award number R01DE024468; National Institute on Aging, award number UH2AG064704; and National Cancer Institute, grant number R21CA260382), the U.S. Department of Energy, Office of Science, Office of Biological \& Environmental Research through the Microbial Community Analysis and Functional Evaluation in Soils SFA Program (m-CAFEs) under contract number DE-AC02-05CH11231 to Lawrence Berkeley National Laboratory, the National Science Foundation (grants 1457695, NSFOCE-BSF 1635070 and the NSF Center for Chemical Currencies of a Microbial Planet) and the Human Frontiers Science Program (RGP0020/2016 and RGP0060/2021).
DK acknowledges support by the Kilachand Multicellular Design Program graduate fellowship.
KSK was supported by Simons Foundation Grant \#409704, by the Research Corporation for Science Advancement through Cottrell Scholar Award \#24010, by the Scialog grant \#26119, and by the Gordon and Betty Moore Foundation grant \#6790.08.

\section*{Contributions}
Designed the research project: DK, KK, DS, ZH, CDL. Performed analysis: DK, GB. Wrote the first draft of the manuscript: DK. Revised and wrote the final version of the manuscript: DK, DS, KK.
